---
title: "report0"
format: html
---

# Description

This quarto file was produced during the EcoStat cours in Montpellier as part of the excercise 4 on Targets. This file is supposed to be integrated in the target pipeline. To make things smooth, small chunks of code should only incude calls to the 'tar_target' functions defined in my targettest.R file.

# Beforehand

## Packages

These are the packages I used for my file **test_targets.R** file.

```{r}
# library(targets)
# library(tarchetypes)
# library(ggplot2)
# library(visNetwork)
```

These are the packages I might use this file *.qmd*.

## Setup

These are the parameters to apply to this whole document (**report_targets.qmd**).

```{r}
#| label: setup
#| echo: false
#| include: false
#| eval: true
#| message: false
#| collapse: true

library(targets)
```

# Calling the targets


```{r}
#| label: loading-data

tar_load(table1)
table2 <- tar_read(table2)
table3 <- tar_read(table3)
big_table <- tar_read(big_table)
```

Read Tables

```{r}

knitr::kable(head(table1, 10), 
             caption = paste("Table 1: list of mammals"))
             
knitr::kable(head(table2, 10),
             caption = paste("Table 2: mammals in ecoregions"))

knitr::kable(head(table3, 10),
             caption = paste("Table 3: list of ecoregions"))
```

Subset only the Ursidae family from table1

```{r}
tar_load(ursidae)
```

Merge all tables in one "big table" and show

```{r}
knitr::kable(head(big_table, 10),
             caption = paste("Table 3: list of ecoregions"))
```

Count the ecoregions from big table

```{r}
tar_load(count_ecoreg)
```

Plot in how many ecoregions eqch species is present

```{r}
tar_load(plot)
```

Plot the targets scheme

```{r}
targets::tar_visnetwork()
```
